References

### 2015-01-05 cv/SecondApplicationToKU.tex
Added CV and cover letters.

%----------------------------------------------------------------------------------------

\begin{document}
\begin{newlfm}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

I understand from your department's website that you are offering Ph.D
stipends, and found it a truly exciting opportunity. I have hence
contacted Prof. Thomas Valentin Mikosch and asked for his
supervision. After a kind discussion with me about my master's 
thesis, his research area, and a very interesting Ph.D project in
random matrix theory (RMT) and extreme value theory (EVT), he
encouraged me to apply. The project that he outlined perfectly
continued my master's studies and I really look forward to it. So I
would like to present to you what I did as my master's thesis project
and what my research interests are.

I wrote my thesis under the supervision of Prof. Sven \AA berg at Lund
university in the department of mathematical physics. I first compared
GARCH and stochastic volatility (SV) models by case studying of
intraday returns of a few Swedish stocks, and then I continued to
study the covariance matrix of Gaussian and GARCH(1,1) returns. There
I encountered the problem of eigenvalues distribution of a Wishart
matrix and found its large and charming literature.

By numerical simulation, I studied in the cases of Gaussian and
GARCH(1,1) returns, how the matrix elements and eigenvalues were
distributed, how the eigenvectors were composed, and in particular,
how the situation was changed by autocorrelations in the return
series. For example, I found in the case of GARCH(1,1) returns that
prolonged return series increased the extent of the eigenvectors'
localization while strengthened autocorrelations decreased the extent
of localization.

Among the many fascinating things that I was led to by the thesis
project were the extreme value theory and the random matrix
theory. In my studies of the intraday stock returns, heavy-tailed
distributions, and in particular L\'evy distributions, are very
important, so I read books such as ``Modeling Extremal Events'',
``Handbook of Financial Time Series'', and papers about the tail
behavior of GARCH and SV models, as well as those on the eigenvalues
distribution of random matrices. Quite naturally, these books and
papers led me to Prof. Mikosch. So when I met him and he outlined the
Ph.D project on RMT and EVT, which followed directly from my master's
project, I knew it was truly a great opportunity for me.

If I am so honored to be accepted, I will, first of all, learn more
about EVT in connection with multivariate time 
series, and also about its application in the research of RMT. Then I
would like to explore, for example, if and how the methods developed in the
research of the largest eigenvalue distribution and the spectral
density of random matrices, particularly Wishart matrices, can
be applied, presumably with EVT, to find the eigenvalues distribution
of a covariance matrix of heavy-tailed returns, such as those generated
by GARCH or SV models.

In particular, I understand that the problem of the exact
distribution of the largest eigenvalue of a Wishart matrix has been
attacked by the holonomic gradient method as an alternative to the
more conventional approach of series expansion around the origin. It
would be interesting to see if the same methods are applicable to the
aforementioned problem.

I look forward to an interview with you. If you would like to know more
about me, you are most welcome to call me at +46 70 489 0472 or find
me on LinkedIn as ``Xie Xiaolei''. If you want to contact my thesis
supervisor, Prof. Sven \AA berg, he is reachable via telephone +46 46
222 96 33 or mobile +46 70 557 35 69.

>>>>

%------------------------------------------------

\begin{document}
\begin{newlfm}
I am currently a self-financing Ph.D student under the supervision of
Prof. Thomas Mikosch. I understand that the department is providing
free stipends to Ph.D students, so I would like to apply for a grant.

I started the Ph.D program here on 1st of October and have been taking
the courses {\it Extreme Value Theory} given by Prof. Mikosch and {\it
  Quantitative Risk Management} given by Prof. Collamore. At the same
time I have done analysis on the eigenvalues of empirical covariance
matrices of the S\&P500 and the DAX indices. A detailed plan of my
Ph.D program is submitted along with this application.

I obtained my master's degree in mathematical physics from Lund
University, with a thesis on econophysics supervised by Prof. Sven \AA
berg. Based on the results of the thesis and with some continued work,
Prof. \AA berg and I have written a paper together under the title
``Effect of Heteroscedasticity on the spectrum of an Empirical
Covariance Matrix'' and plan to submit it to {\it Quantitative
  Finance} for publication. In the paper we argued that, on certain
conditions, autocorrelations in the conditional volatilities could
affect the empirical covariance matrixes' spectrum only through the
unconditional distribution of the volatilities. On these
conditions, we derived in the case of small autocorrelations the
spectrum of an empirical covariance matrix. The derivations were based
on results from free probability theory.

Without a stipend, I am living on my own savings and borrowed money
from my relatives. This admittedly causes hardships and
distractions. So I really hope a stipend can be granted to me. It
would be a great ease not only to me but also to my family. Thank you
for your consideration.

### 2015-01-05 cv/XieXiaolei-Academic.tex
Added CV and cover letters.

\begin{minipage}[t]{0.5\textwidth}
  Citizenship: Sweden \\
  Phone: +46 70 489 0472 \\
  Email: \href{mailto:xie.xiaolei@gmail.com}{\tt xie.xiaolei@gmail.com} \\
  Address: Kiviksgatan 7C, 21440 Malm\"{o}, Sweden
\end{minipage}

\section*{Education}
\begin{itemize}
\item Master of Physics, Lund University, January 2011 - June 2014.
  \begin{itemize}
  \item {\it Major Subject:} Econophysics. My thesis project was
    case studying of intraday returns of Nordea, Volvo and
    Ericsson. Covariance matrices of GARCH and stochastic volatility
    returns were also studied. Matlab programming was a crucial part.
  \end{itemize}
\item M.Sc.(Tech) Computer Science and Engineering, Helsinki
  University of Technology, 2005 - 2008.
  \begin{itemize}
  \item {\it Major Subject:} Mobile Computing - Services and Security
  \item {\it Average grade:} 4.17/5.
  \end{itemize}
\item B.Sc. Computer Science \& Technology, Beijing Institute of
  Technology, 2001- 2005.
  \begin{itemize}
  \item {\it Average grade:} 85.5/100.
  \item {\it Honors:} \textit{Distinguished Graduates of 2005}.
  \end{itemize}
\end{itemize}

\section*{Employment}
\begin{aperiod}
\item {\it \href{http://www.stericsson.com}{\tt
      ST-Ericsson}, Audio, Multimedia, Development Engineer, Sep 2008
    - Jan 2011}

  My responsibilities included developing audio low-level software,
  typically device drivers, in the Linux OS. This involved designing and
  implementing data structures and procedures so that the hardware
  devices were used in the optimal way, in terms of parallelism,
  power consumption, robustness, and ease of maintenance.

\item {\it \href{http://www.hiit.fi}{\tt Helsinki
      Institute of Information Technology}, Thesis Worker, Oct 2007 -
    May 2008}

  Funded by HIIT, I wrote my thesis ``A Mutual authentication and Key
  Agreement Protocol for the UMTS Network''. The algorithm of my
  protocol proposal was based on the Diffie-Hellman Exchange, but had
  significant modifications and extensions so that the mutual
  authentication between the mobile user and the network was delegated
  to the serving instead of the home network. The protocol design
  incorporated puzzle schemes that demanded unbalanced computing
  resources on the two sides to mitigate Denial-of-Service attacks. I
  made C programs to test the puzzle schemes.

\item {\it
    \href{http://www.goodmillsystems.com}{\tt Goodmillsystems},
    Software Designer, May 2007 - Sep 2007}

  I developed a daemon program that ran on the company's smart router
  product to collect statistical data about the router's network
  traffic. The emphasis of the program was high performance in the
  context of competing read and write accesses.

\item {\it \href{http://www.cardinal.fi/}{\tt
      Cardinal Information Systems}, Software Developer, Sep 2006 -
    April 2007}

  I implemented the FLUTE protocol for the company's DVB-H
  mobile-end middleware. The implementation was multi-threaded and was
  built on the {\it pthread} library. Good performance and robustness
  were crucial requirements on the implementation.

\item {\it
    \href{http://www.digitalchocolate.com/}{\tt Digital Chocolate},
    Game Engineer, Feb 2006 - Sep 2006}

  At this job, my responsibilities were porting and customizing mobile
  phone games for various handsets, and making game demos.

\item {\it {\tt Beijing Holystone Ltd}, Software
    Engineer, April 2004 - June 2005}

  At this job I mainly developed JSP pages and database routines for
  the company's information system.
\end{aperiod}

\section*{Personal Project}
{\it Trades data collector \& Analyzer}

I have been developing my own stock-trading robot since the summer of
2011. It is a software built on cURL, GLib, MySQL, and Matlab. I find
it a fairly interesting, challenging, and rewarding combination of
programming skills, data analysis techniques, and knowledge of
financial time series. My knowledge in econophysics guides the
development of this software.

\section*{Non-English Language Skills}
\begin{itemize}
\item Swedish: informal communications. ``Swedish B'' passed.
\item Chinese: Native speaker
\end{itemize}

>>>>

\begin{minipage}[t]{0.5\textwidth}
  Phone: +46 76 060 6638 \\
  Email: \href{mailto:xie.xiaolei@gmail.com}{\tt xie.xiaolei@gmail.com} \\
  Address: Kiviksgatan 7C, 21440 Malm\"{o}, Sweden
  Citizenship: Sweden \\
\end{minipage}

% \section*{Objective}
% A master of mathematical physics and Computer Science is looking for a
% Ph.D position in the areas of stochastic processes, random matrix
% theory and extreme value theory.

\section*{Education}
\begin{itemize}
\item Master of Physics, Lund University, Sweden, January 2011 - June
  2014.
  \begin{itemize}
  \item {\it Subject:} Mathematical Physics -- econophysics
  \item My thesis project was a specialization in the area of economical
    physics and focused on the influence that auto-correlations in 
    return series had on the spectral distribution of an empirical
    covariance matrix. It was titled ``Return Models and Covariance
    Matrices'' and was supervised by Prof. Sven \AA berg.
  \end{itemize}

\item M.Sc.(Tech) Computer Science and Engineering, Aalto University,
  Finland, 2005 - 2008.
  \begin{itemize}
  \item {\it Major Subject:} Mobile Computing - Services and Security
  \item {\it Average grade:} 4.17/5.
  \item   Funded by HIIT, I wrote my thesis ``A Mutual authentication
    and Key Agreement Protocol for the UMTS Network''. The algorithm of my
    protocol proposal was based on the Diffie-Hellman Exchange, but had
    significant modifications and extensions so that the mutual
    authentication between the mobile user and the network was delegated
    to the serving instead of the home network. The protocol design
    incorporated puzzle schemes that demanded unbalanced computing
    resources on the two sides to mitigate Denial-of-Service attacks. I
    made C programs to test the puzzle schemes.
  \end{itemize}

\item B.Sc. Computer Science \& Technology, Beijing Institute of
  Technology, 2001- 2005.
  \begin{itemize}
  \item {\it Average grade:} 85.5/100.
  \item {\it Honors:} \textit{Distinguished Graduates of 2005}.
  \end{itemize}
\end{itemize}

\section*{Employment}
\begin{itemize}
\item Research Assistant, Lund University, June 10, 2014 - September
  30, 2014

  Based on the results from my thesis work, Prof. \AA berg and I wrote
  a paper together. Titled ``Effect of Heteroscedasticity on the
  spectrum of an Empirical Covariance Matrix'', we argued that, in
  certain circumstances, autocorrelations in the conditional
  volatilities were manifest in the empirical covariance matrixes'
  spectrum only through the unconditional distribution of the
  volatilities. In these circumstances, we derived in the case of small
  autocorrelations the spectrum of an empirical covariance matrix. The
  derivations were based on results from free probability theory.

\item Software Engineer, April 2004 - January 2011, Helsinki

I worked in the IT industry as a software engineer. I designed and
implemented software solutions in C, C++ and Java.

\end{itemize}

\section*{Skills}
\begin{itemize}
\item {\bf Programming:} Proficient in C, C++, Java, Matlab
\item {\bf Scientific writing:} Latex
\end{itemize}

\section*{Association}
I am a professional member of the {\it Association of Computing Machinery}.

\section*{Referees}
\begin{itemize}
\item Prof. Sven \AA berg. Email:
  \href{mailto:sven.aberg@matfys.lth.se}{\tt
    sven.aberg@matfys.lth.se}. Telephone: +46 46 222 96 33. Mobile:
  +46 70 557 35 69.

\item Prof. Ferdi
  Aryasetiawan. Email: \href{ferdi.aryasetiawan@teorfys.lu.se}{\tt
    ferdi.aryasetiawan@teorfys.lu.se}. Telephone: +46 46 222 90 89.
\end{itemize}
